The imprint of global magma oceans on exoplanet demographics

### 2023-03-17 src/tex/ms.tex
add a table with all key parameters and assumptions

@@

\subsection{Influence of different mass-radius relationships on our results}\ref{app:MR_relation}
We assessed how a different choice of baseline mass-radius relation influences our results.
Focussing on the detectability of the statistical runaway greenhouse signal and the ability to constrain the threshold instellation, we repeated the hypothesis test in Sect.~\ref{sec:res_testability} with alternative mass-radius relationships.
Instead of assuming a pure $\mathrm{MgSiO_3}$ composition, we assigned planet masses using either the probabilistic relationship in \citet{Wolfgang2016} or a semi-empirical, two-layer relation assuming an Earth-like (\SI{32.5}{\percent} Fe + \SI{67.5}{\percent} MgSiO$_3$) composition~\citep{Zeng2016}.

>>>>

% include table with key parameters
\input{table_parameters}

@@

\subsection{Influence of different mass-radius relationships on our results}\label{app:MR_relation}
We assessed how a different choice of baseline mass-radius relation influences our results.
Focussing on the detectability of the statistical runaway greenhouse signal and the ability to constrain the threshold instellation, we repeated the hypothesis test in Sect.~\ref{sec:res_testability} with alternative mass-radius relationships.
Instead of assuming a pure $\mathrm{MgSiO_3}$ composition, we assigned planet masses using either the probabilistic relationship in \citet{Wolfgang2016} or a semi-empirical, two-layer relation assuming an Earth-like (\SI{32.5}{\percent} Fe + \SI{67.5}{\percent} MgSiO$_3$) composition~\citep{Zeng2016}.
